Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2017-12-15 Ben_Manuscripts/structure_paper/Draft.tex
First draft pretty much done

  \begin{figure}
	\centering
	\begin{subfigure}{.3\textwidth}
		\centering
		%\includegraphics[width=\linewidth, trim={2.5cm 0 4cm 1.25cm}, clip]{WAXS_raw.png}
		\includegraphics[width=\textwidth]{NaGA3C11.png}
		\caption{}~\label{fig:monomer}
	\end{subfigure}
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{monomer_twocolor.png}
		\caption{}~\label{fig:atomistic_monomer}
	\end{subfigure}
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{wedge.png}
		\caption{}~\label{fig:wedge}
	\end{subfigure}
		\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{layer_blender.png}
		\caption{}~\label{fig:wedge_layer}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{hexagonal_packing.png}
		\caption{}~\label{fig:hex_packing_simple}
	\end{subfigure}
	\caption{The liquid crystal monomer Na-GA3C11 (a) rendered atomistically (b)
	exhibits wedge-like character (c). Monomer wedges assemble into disks (d) with
	hydrophilic head groups (blue) facing towards the disk center. The disks
	assemble into hexagonally packed columnnar mesophases (e)}~\label{fig:assembly}
  \end{figure}

@@

  A molecular level understanding of LLC membrane structure, enabled by
  molecular dynamics simulations, will provide guidelines to reduce the large
  chemical space available to design monomers for creation of separation-specific
  membranes. A good molecular model should incorporate a detailed picture of the
  nanoscopic pore structure which will be crucial to understanding the role of
  monomer structure in solute transport and membrane design. Models resulting
  from molecular dynamics simulations will provide the required level of detail.
  We can directly observe solute transport and suggest governing mechanisms. We
  can observe how the choice of head group may influence pore size for size
  exclusion driven separations. We can interchange counterions which may
  influence both the pore size and the strength of the Donnan potential which
  affects the degree to which the membrane can exclude charged species.

  % BJC: improve this figure
  \begin{figure}
  \centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{nanopore_undetailed.jpg}
		\caption{}~\label{fig:undetailed_pore}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{detailed_pore.png}
		\caption{}~\label{fig:detailed_pore}
	\end{subfigure}
  \caption{(a) Our previous understanding of the pore structure allows us to speculate
	   about separation behavior. (b) A detailed molecular model will allow us to
	   directly observe solute transport. Here, four stacked layers of 5 monomers
           are pictured atomistically. The hydrophilic region is in red and the 
	   hydrophoic region is colored blue.}~\label{fig:detail}
  \end{figure}

@@

  \begin{figure}
        \centering
        \begin{subfigure}[t]{0.43\linewidth}
                \centering
                \includegraphics[width=\linewidth]{SAXS.png}
                \caption{}\label{fig:SAXS}
        \end{subfigure}
        \begin{subfigure}[t]{0.47\linewidth}
                \centering
                \includegraphics[width=\linewidth]{WAXS_annotated.png} 
                \caption{}\label{fig:WAXS}
        \end{subfigure}
	\caption{(a) The repeat spacing in the 1D small angle X-ray scattering pattern
		is characteristic of hexagonal packing. The leading peak represents the
		distance between the d\textsubscript{100} planes. Using this distance, we know
		that the distance between pore centers is 4.12 nm. (b) 2D wide angle X-ray
		scattering gives details about repeating features less than 1 nanometer
		apart. Experimentalists have justified each of the 5 major reflections
		present as follows: (I) Aromatic head group $\pi-\pi$ stack 3.7 \AA~apart.
		(II) Monomers arrange vertically in a 2\textsubscript{1} helix. (III) Alkane
 		chain tails pack 4.5 \AA~apart. (IV) Monomer tails tilt with respect to the 
 		membrane plane. (V) As derived from SAXS, pores pack hexagonally and are 
		spaced 4.12 nm apart}
	\label{fig:SWAXS}
 \end{figure}

@@

  \begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
	\caption{(a) A single monomer was parameterized and annealed to produce a low energy
		configuration. (b) Monomers are rotated and assembled into layers with 
		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
		a pore. (d) Pores are duplicated and placed into a monoclinic unit cell}\label{fig:python}
  \end{figure}

@@

@@

  \begin{figure}
        \centering
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{zdf_overlay_layered.png}
                \caption{}\label{fig:zdf_layered}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{zdf_overlay_offset.png}
                \caption{}\label{fig:zdf_offset}
        \end{subfigure}
        \caption{Pair distribution functions of aromatic carbons for the
        (a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer,
        parallel displaced configurations. Clear periodic maxima in the
        $z$ number density indicate distinct layers. The magnitude
        of the spikes with respect to the average suggest that the 5
        monomer per layer, sandwiched configuration possesses a higher
        degree of layer partitioning.}\label{fig:zdf}
  \end{figure}

@@

  The parallel displaced configuration results in a simulated XRD pattern with
  the closest match to experiment. It produces the only pattern that exhibits
  all major reflections. R-alkanes, R-pores and R-$\pi$ appear as they do in the
  sandwiched configuration. R-spots appears, however with a lower intensity
  relative to R-alkanes when compared to the sandwiched configuration. R-helix
  appears due to the parallel displaced aromatic rings. It is a subharmonic
  of R-$\pi$ since the nearest vertically stacked head group to any given head
  group is 7.4 \AA~ away.

  \begin{figure}
  \begin{subfigure}{0.3\linewidth}
        \centering
        \vspace{-0.2em}
        \includegraphics[width=1.018\linewidth]{layered_rzplot.png}
        \caption{}~\label{fig:rz_layered}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
        \centering
        \vspace{0.25em}
        \includegraphics[scale=0.0987]{WAXS_raw.png}
        \caption{}~\label{fig:raw_waxs}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
        \centering
        \includegraphics[width=\linewidth]{offset_rzplot.png}
        \caption{}~\label{fig:rz_offset}
  \end{subfigure}
  \begin{subfigure}{0.0544\linewidth}
        \centering
        \vspace{-3.30em}
        \includegraphics[width=\linewidth]{colorbar_jet.png}
  \end{subfigure}
  \caption{The simulated X-ray diffraction patterns for simulations run in the
  sandwiched (a) and parallel-displaced (c) configurations are compared to experiment (b). 
  The parallel displaced configuration is the only one that exhibits all major
  reflections of interest to some degree}
  \label{fig:XRDsim}
  \end{figure}

@@

  \begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
  \caption{The tilt angle distribution of alkane chain tails with respect to the membrane plane
  indicates an average tilt angle near 7\degree which is far from the 37\degree tilt angle 
  previously used to explain R-spots}~\label{fig:tilt}
  \end{figure}

@@

  \begin{figure}
	\centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{tails_topview.png}  % picture of top of unit cell with only tail atoms shown
		\caption{}\label{fig:topdown_tails_only}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{tails_rzplot.png}
		\caption{}\label{fig:tails_rzplot}
	\end{subfigure}
	\caption{(a) All atoms except carbon atoms making up the tails are removed from the 
	trajectory. (b) The simulated diffraction pattern of the tail-only trajectory still 
        shows R-spots}\label{fig:tails}
  \end{figure}

@@

  Structural properties are different when layers are initially spaced 5 \AA~
  apart. In both configurations, we observe a decrease in pore spacing
  (Fig.~\ref{fig:p2p_disordered}) and a corresponding increase in the equilibrated
  distance between layers (Fig.~\ref{fig:dbwl_disordered}). The simulated X-ray
  diffraction patterns indicate further structural differences. In the parallel
  displaced configuration, R-spots fades to the point that it is indistinguisable
  from R-alkanes (Fig. ~\ref{fig:offset_disordered_xrd}). In the sandwiched
  configuration, R-spots is present in different locations, showing higher
  intensity at the top and bottom of the pattern as well as at the intersection
  of R-alkanes with q$_z$ = 0 (Fig. ~\ref{fig:layered_disordered_xrd}).

@@

  \begin{figure}[!hbt]
        \centering
        \begin{subfigure}{0.45\linewidth}
                \centering
                \includegraphics[width=\linewidth]{dbwl.png}
                \caption{}~\label{fig:dbwl_disordered}
        \end{subfigure}%
        \begin{subfigure}{0.45\linewidth}
                \centering
                \includegraphics[width=\linewidth]{p2p2.png}
                \caption{}~\label{fig:p2p_disordered}
        \end{subfigure}
        \begin{subfigure}{0.45\linewidth}
                \centering
                \includegraphics[width=\linewidth]{offset_disordered_rzplot.png}
                \caption{}~\label{fig:offset_disordered_xrd}
        \end{subfigure}%
        \begin{subfigure}{0.45\linewidth}
                \centering
                \includegraphics[width=\linewidth]{layered_disordered_rzplot.png}
                \caption{}~\label{fig:layered_disordered_xrd}
        \end{subfigure}
	\caption{In comparison to systems built with 3.7 \AA initial layer spacing,  
                the simulated X-ray diffraction patterns of the parrallel displaced (a) and 
 		sandwiched (b) configurations are different when systems are built with 
 		a 5 \AA initial layer spacing, most notably in the region bounded by R-alkanes.
      		When layers are stacked further apart, the distance between layers increases (c)
                and the pore spacing decreases (d).}
  \end{figure}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{offset_density.png}
        \caption{}
        \label{fig:offset_density}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{layered_density.png}
        \caption{}
        \label{fig:layered_density}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{disordered_offset_density.png}
        \caption{}
        \label{fig:disordered_offset_density}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{disordered_density.png}
        \caption{}
        \label{fig:disorder_layered_density}
  \end{subfigure}
  \caption{In all cases, assemblies stay partitioned into hydrophilic and
	  hydrophobic regions. The parallel displaced (a), the disordered parallel
	  displaced (c), and the disordered sandwiched (d) show similar pore structures.
	  The sandwiched configuration (b) exhibits an open pore structure with sodium
	  ions and head groups concentrated away from the pore
	  center.}~\label{fig:densities}
  \end{figure}

@@

  \begin{figure}
	\centering
	\includegraphics[width=\textwidth]{solvation.png}  % still working on formatting so this is a screenshot of a doctored latex figure
        %MRS2: include 0% as well? Maybe leave off 5% if not relevant in the end?
	\caption{}
	\label{fig:solvation}
  \end{figure}

@@

  \begin{figure}
  \centering 
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{offset_solvated_density.png}
        \caption{}
        \label{fig:offset_solvated_density}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{layered_solvated_density.png}
        \caption{}
        \label{fig:layered__solvated_density}
  \end{subfigure}
  \caption{Water fills the membrane pores in the parallel displaced (a) and 
  sandwiched (b) configurations. Sodium ions are distributed more uniformly 
  in the sandwiched configuration.}
  \label{fig:water_density}
  \end{figure}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{rzplot_xlink.png}
	\caption{}~\label{fig:rzplot_xlink}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{IC_xlink.png}
	\caption{}~\label{fig:IC_xlink}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{dbwl_xlink.png}
	\caption{}~\label{fig:dbwl_xlink}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{p2p_xlink.png}
	\caption{}~\label{fig:p2p_xlink}
  \end{subfigure}
  \caption{(a) Reflections produced by the crosslinked configuration fade relative
  to the uncrosslinked system. The colorbar shown is the same used for the uncrosslinked
  system. (b) The ionic conductivity is smaller relative to the uncrosslinked system, but
  still much larger than the experimental value. (c) The distance between layers increases
  when the system is crosslinked. (d) The pore spacing decreases when the membrane is 
  crosslinked.}~\label{fig:xlink}
  \end{figure}

>>>>

  %BJC: TODO: Scalable vector graphic for monomer structure, make bigger. Convert .svg to .eps
  %           Thicken slabs
  %           Make pore region on slab (blue) bigger
  %           Bump up atom sizes in atomistic render
  \begin{figure}
	\centering
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{NaGA3C11.png}
		\caption{}~\label{fig:monomer}
	\end{subfigure}
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{monomer_twocolor.png}
		\caption{}~\label{fig:atomistic_monomer}
	\end{subfigure}
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{wedge.png}
		\caption{}~\label{fig:wedge}
	\end{subfigure}
		\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{layer_blender.png}
		\caption{}~\label{fig:wedge_layer}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{hexagonal_packing.png}
		\caption{}~\label{fig:hex_packing_simple}
	\end{subfigure}
	\caption{The liquid crystal monomer Na-GA3C11 (a) rendered atomistically (b)
	exhibits wedge-like character (c). Monomer wedges assemble into disks (d) with
	hydrophilic head groups (blue) facing towards the disk center. The disks
	assemble into hexagonally packed columnnar mesophases (e)}~\label{fig:assembly}
  \end{figure}

@@

  A molecular level understanding of LLC membrane structure, enabled by
  molecular dynamics simulations, will provide guidelines to reduce the large
  chemical space available to design monomers for creation of separation-specific
  membranes. A good molecular model should incorporate a detailed picture of the
  nanoscopic pore structure which will be crucial to understanding the role of
  monomer structure in solute transport and membrane design. Models resulting
  from molecular dynamics simulations will provide the required level of detail (Fig. \ref{fig:detail}).
  We can directly observe solute transport and suggest governing mechanisms. We
  can observe how the choice of head group may influence pore size for size
  exclusion driven separations. We can interchange counterions which may
  influence both the pore size and the strength of the Donnan potential which
  affects the degree to which the membrane can exclude charged species.

  % BJC: TODO: Make new rendering of wedges
  %            Change color scheme 
  \begin{figure}
  \centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{nanopore_undetailed.jpg}
		\caption{}~\label{fig:undetailed_pore}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{detailed_pore.png}
		\caption{}~\label{fig:detailed_pore}
	\end{subfigure}
  \caption{(a) Our previous understanding of the pore structure allows us to speculate
	   about separation behavior. (b) A detailed molecular model will allow us to
	   directly observe solute transport. Here, four stacked layers of 5 monomers
           are pictured atomistically. The hydrophilic region is in red and the 
	   hydrophoic region is colored blue.}~\label{fig:detail}
  \end{figure}

@@

  %BJC: TODO: update colorbar
  \begin{figure}
        \centering
        \begin{subfigure}[t]{0.43\linewidth}
                \centering
                \includegraphics[width=\linewidth]{SAXS.png}
                \caption{}\label{fig:SAXS}
        \end{subfigure}
        \begin{subfigure}[t]{0.47\linewidth}
                \centering
                \includegraphics[width=\linewidth]{WAXS_annotated.png} 
                \caption{}\label{fig:WAXS}
        \end{subfigure}
	\caption{(a) The repeat spacing in the 1D small angle X-ray scattering pattern
		is characteristic of hexagonal packing. The leading peak represents the
		distance between the d\textsubscript{100} planes. Using this distance, we know
		that the distance between pore centers is 4.12 nm. (b) 2D wide angle X-ray
		scattering gives details about repeating features less than 1 nanometer
		apart. Experimentalists have justified each of the 5 major reflections
		present as follows: (I) Aromatic head group $\pi-\pi$ stack 3.7 \AA~apart.
		(II) Monomers arrange vertically in a 2\textsubscript{1} helix. (III) Alkane
 		chain tails pack 4.5 \AA~apart. (IV) Monomer tails tilt with respect to the 
 		membrane plane. (V) As derived from SAXS, pores pack hexagonally and are 
		spaced 4.12 nm apart}
	\label{fig:SWAXS}
 \end{figure}

@@

  %BJC: TODO: reproduce figure in latex (or gimp?) with higher resolution arrows
  \begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
	\caption{(a) A single monomer was parameterized and annealed to produce a low energy
		configuration. (b) Monomers are rotated and assembled into layers with 
		hydrophlic centers. (c) Twenty layers are stacked on top of each other to create
		a pore. (d) Pores are duplicated and placed into a monoclinic unit cell}\label{fig:python}
  \end{figure}

@@

  The colorbars on all diffraction patterns are normalized relative to
  R-alkanes. We calculated the average intensity within R-alkanes of the
  experimental pattern, $I_{avg}$.  We exclude intensities within $\pm$
  30\degree~of the $q_r=0$ axis, since the simulated patterns differ from
  experiment in those regions (See Fig. \ref{fig:XRDsim}).  We multiplied $I_{avg}$
  by a scaling factor of 2.5.  Intensities that appear in the experimental
  pattern $\geq$ 2.5$*I_{avg}$ receive colorbar values of 1. The result of this
  colorbar scaling method is shown in Figure \ref{fig:WAXS}. We apply the same
  scaling method to the simulated patterns.

@@

  %BJC: TODO: increase font size on legends
  \begin{figure}
        \centering
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{zdf_overlay_layered.png}
                \caption{}\label{fig:zdf_layered}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{zdf_overlay_offset.png}
                \caption{}\label{fig:zdf_offset}
        \end{subfigure}
        \caption{Pair distribution functions of aromatic carbons for the
        (a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer,
        parallel displaced configurations. Clear periodic maxima in the
        $z$ number density indicate distinct layers. The magnitude
        of the spikes with respect to the average suggest that the 5
        monomer per layer, sandwiched configuration possesses a higher
        degree of layer partitioning.}\label{fig:zdf}
  \end{figure}

@@

  The parallel displaced configuration results in a simulated XRD pattern with
  the closest match to experiment. It produces the only pattern that exhibits all
  major reflections. R-alkanes and R-pores appear as they do in the
  sandwiched configuration. R-spots and R-$\pi$ appears, however with a lower intensity relative to
  R-alkanes when compared to the sandwiched configuration. R-helix appears due to
  the parallel displaced aromatic rings. It is a subharmonic of R-$\pi$ since the
  nearest vertically stacked head group to any given head group is 7.4 \AA~ away.

  %BJC: adjust figure size and alignment -- probably easiest to set figure size in matplotlib
  \begin{figure}
  \begin{subfigure}{0.3\linewidth}
        \centering
        \vspace{-0.2em}
        \includegraphics[width=1.018\linewidth]{layered_rzplot.png}
        \caption{}~\label{fig:rz_layered}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
        \centering
%        \vspace{0.25em}
        \includegraphics[scale=0.29]{WAXS_raw.png}
        \caption{}~\label{fig:raw_waxs}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
        \centering
        \includegraphics[width=\linewidth]{offset_rzplot.png}
        \caption{}~\label{fig:rz_offset}
  \end{subfigure}
  \begin{subfigure}{0.0544\linewidth}
        \centering
        \vspace{-3.30em}
        \includegraphics[width=\linewidth]{colorbar_jet.png}
  \end{subfigure}
  \caption{The simulated X-ray diffraction patterns for simulations run in the
  sandwiched (a) and parallel-displaced (c) configurations are compared to experiment (b). 
  The parallel displaced configuration is the only one that exhibits all major
  reflections of interest to some degree}
  \label{fig:XRDsim}
  \end{figure}

@@

  \begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
  \caption{The tilt angle distribution of alkane chain tails with respect to the membrane plane
  indicates an average tilt angle near 7\degree~which is far from the 37\degree~tilt angle 
  previously used to explain R-spots.}~\label{fig:tilt}
  \end{figure}

@@

  \begin{figure}
	\centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{tails_topview.png}  % picture of top of unit cell with only tail atoms shown
		\caption{}\label{fig:topdown_tails_only}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{tails_rzplot.png}
		\caption{}\label{fig:tails_rzplot}
	\end{subfigure}
	\caption{(a) All atoms except carbon atoms making up the tails are removed from a 
	sandwiched configuration trajectory. (b) The simulated diffraction pattern of the
        tail-only trajectory still shows R-spots}\label{fig:tails}
  \end{figure}

@@

  Structural properties are different when layers are initially spaced 5 \AA~
  apart. In both configurations, we observe a decrease in pore spacing
  (Fig.~\ref{fig:p2p_disordered}) and a corresponding increase in the equilibrated
  distance between layers (Fig.~\ref{fig:dbwl_disordered}). The simulated X-ray
  diffraction patterns indicate further structural differences. In the parallel
  displaced configuration, almost all contrast between R-spots and R-alkanes is faded
  (Fig. ~\ref{fig:offset_disordered_xrd}). In the sandwiched
  configuration, R-spots is weakly present, but in different locations, showing higher
  intensity at the top and bottom of the pattern as well as at the intersection
  of R-alkanes with q$_z$ = 0 (Fig. ~\ref{fig:layered_disordered_xrd}).

@@

  \begin{figure}[!hbt]
        \centering
        \begin{subfigure}{0.45\linewidth}
                \centering
                \includegraphics[width=\linewidth]{dbwl.png}
                \caption{}~\label{fig:dbwl_disordered}
        \end{subfigure}%
        \begin{subfigure}{0.45\linewidth}
                \centering
                \includegraphics[width=\linewidth]{p2p2.png}
                \caption{}~\label{fig:p2p_disordered}
        \end{subfigure}
        \begin{subfigure}{0.45\linewidth}
                \centering
                \includegraphics[width=\linewidth]{offset_disordered_rzplot.png}
                \caption{}~\label{fig:offset_disordered_xrd}
        \end{subfigure}%
        \begin{subfigure}{0.45\linewidth}
                \centering
                \includegraphics[width=\linewidth]{layered_disordered_rzplot.png}
                \caption{}~\label{fig:layered_disordered_xrd}
        \end{subfigure}
	\caption{In comparison to systems built with 3.7 \AA~ initial layer spacing,  
                the simulated X-ray diffraction patterns of the parrallel displaced (a) and 
 		sandwiched (b) configurations are different when systems are built with 
 		a 5 \AA~ initial layer spacing, most notably in the region bounded by R-alkanes.
      		When layers are stacked further apart, the distance between layers increases (c)
                and the pore spacing decreases (d).}
  \end{figure}

@@

  % BJC: TODO: Increase font size
  %            Put insets in the figures that make it clear what configuration each represents
  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{offset_density.png}
        \caption{}
        \label{fig:offset_density}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{layered_density.png}
        \caption{}
        \label{fig:layered_density}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{disordered_offset_density.png}
        \caption{}
        \label{fig:disordered_offset_density}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{disordered_density.png}
        \caption{}
        \label{fig:disorder_layered_density}
  \end{subfigure}
  \caption{In all cases, assemblies stay partitioned into hydrophilic and
	  hydrophobic regions. The parallel displaced (a), the disordered parallel
	  displaced (c), and the disordered sandwiched (d) show similar pore structures.
	  The sandwiched configuration (b) exhibits an open pore structure with sodium
	  ions and head groups concentrated away from the pore
	  center.}~\label{fig:densities}
  \end{figure}

@@

  % BJC: TODO: reformat
  %            adjust colorbar
  \begin{figure}
	\centering
	\includegraphics[width=\textwidth]{solvation.png}  % still working on formatting so this is a screenshot of a doctored latex figure
        %MRS2: include 0% as well? Maybe leave off 5% if not relevant in the end?
	\caption{}
	\label{fig:solvation}
  \end{figure}

@@

  %BJC: TODO: Bigger fonts
  \begin{figure}
  \centering 
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{offset_solvated_density.png}
        \caption{}
        \label{fig:offset_solvated_density}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
        \includegraphics[width=1\linewidth]{layered_solvated_density.png}
        \caption{}
        \label{fig:layered__solvated_density}
  \end{subfigure}
  \caption{Water fills the membrane pores in the parallel displaced (a) and 
  sandwiched (b) configurations. Sodium ions are distributed more uniformly 
  in the sandwiched configuration.}
  \label{fig:water_density}
  \end{figure}

@@

  %BJC: add units
  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{rzplot_xlink.png}
	\caption{}~\label{fig:rzplot_xlink}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{IC_xlink.png}
	\caption{}~\label{fig:IC_xlink}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{dbwl_xlink.png}
	\caption{}~\label{fig:dbwl_xlink}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{p2p_xlink.png}
	\caption{}~\label{fig:p2p_xlink}
  \end{subfigure}
  \caption{(a) Reflections produced by the crosslinked configuration fade relative
  to the uncrosslinked system. The colorbar shown is the same used for the uncrosslinked
  system. (b) The ionic conductivity is smaller relative to the uncrosslinked system, but
  still much larger than the experimental value. (c) The distance between layers increases
  when the system is crosslinked. (d) The pore spacing decreases when the membrane is 
  crosslinked.}~\label{fig:xlink}
  \end{figure}
